Glyph-maps for Visually Exploring Temporal Patterns in Climate Data and Models

### 2012-05-14 revision-final/paper.tex
fixed wraps

\noindent where $\alpha_x, \alpha_y$ are scale parameters setting the fraction the width $w$ and height $h$ of the glyph, respectively. For gridded data, $w$ and $h$ will be the minimum difference between neighboring spatial locations to make use of the resolution of the major components. For irregularly gridded data, $w$ and $h$ would be set to minimize overlap between glyphs.

@@

\noindent where $(t, z)$ have been scaled into the range $[0, 1]$. This is a non-standard conversion to polar coordinates, but it creates a timeline that starts at 12 o'clock and proceeds clockwise. \citet{eden:2010} wraps the time series, overplotting the multiple years, and this could be done also, by adjusting the scale of $t$.

>>>>

\noindent where $\alpha_x, \alpha_y$ are scale parameters setting the fraction of width, $w$, and height, $h$, of the glyph, respectively. For gridded data, $w$ and $h$ will be the minimum difference between neighboring spatial locations to make use of the resolution of the major components. For irregularly gridded data, $w$ and $h$ would be set to minimize overlap between glyphs.

@@

\noindent where $(t, z)$ have been scaled into the range $[0, 1]$. This is a non-standard conversion to polar coordinates, but it creates a timeline that starts at 12 o'clock and proceeds clockwise. \citet{eden:2010} wrap the time series, overplotting the multiple years, and this could be done also, by adjusting the scale of $t$.
